% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org

% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca

% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com

% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}

\newlength{\outerbordwidth}

\pagestyle{empty}

\raggedbottom

\raggedright

\usepackage[svgnames]{xcolor}

\usepackage{framed}

\usepackage{tocloft}

%-----------------------------------------------------------

%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars

\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)

\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------

%Margin setup

\setlength{\evensidemargin}{-0.25in}

\setlength{\headheight}{-0.25in}

\setlength{\headsep}{0in}

\setlength{\oddsidemargin}{-0.25in}

\setlength{\paperheight}{11in}

\setlength{\paperwidth}{8.5in}

\setlength{\tabcolsep}{0in}

\setlength{\textheight}{9.75in}

\setlength{\textwidth}{7in}

\setlength{\topmargin}{-0.3in}

\setlength{\topskip}{0in}

\setlength{\voffset}{0.1in}

%-----------------------------------------------------------

%Custom commands

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{\vspace{8pt}

  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}

    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}

    \end{shaded}

  }\vspace{-5pt}

}

\newcommand{\ressubheading}[4]{

\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}

		\textbf{#1} & #2 \\

		\textit{#3} & \textit{#4} \\

\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{\Large Shad Gregory} & \textbf{\today} \\

captshadg@gmail.com & http://shadgregory.net\\
6280 McNeil Dr Apt 1214 & https://github.com/shadgregory\\
Austin TX 78729 \\

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Development:} Perl, Java, Ruby, JavaScript, JQuery, ExtJS, Scheme

\item I am experienced in a variety of software environments.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Work Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item

	\ressubheading{NextGen Inpatient/Opus Healthcare Inc.}{Austin, TX}{Software Engineer}{2005-PRESENT}

	\begin{itemize}

		\resitem{Developed rich internet web applications in \texttt{Perl} and \texttt{javascript}}
                \resitem{Developed \texttt{Watir} testing scripts in \texttt{Ruby}}

	\end{itemize}

\item

	\ressubheading{DOE Joint Genome Institute (Lawrence Berkeley National Lab)}{Walnut Creek, CA}{Researcher in Analysis Group under Dr. Zhong Wang}{Summer 2010}

	\begin{itemize}

		\resitem{Created \textbf{open source} genome validation software tool in \texttt{python} and \texttt{C}}

    \resitem{Used machine learning to mine TBs of genome data efficiently using novel likelihood function}

	\end{itemize}

\item 

	\ressubheading{Los Alamos National Laboratory}{Los Alamos, NM}{Researcher in Metagenomics Group under Dr. Nick Hengartner}{Summer 2009}

	\begin{itemize}

		\resitem{Wrote \textbf{open source} alignment algorithm software tool in \texttt{python}, \texttt{C} and \texttt{CUDA}}

    \resitem{Used statistical models to discover sequence alignments using parallel algorithms on GPUs}

	\end{itemize}

\item

	\ressubheading{Oregon State University}{Corvallis, OR}{Research Assistant under Prof. Malgorzata Peszynska and Prof. Rubin Landau}{2005-2008}

	\begin{itemize}

		\resitem{Finite element analysis with uncertainty and web-based teaching in \texttt{Java}}

	\end{itemize}

\item

	\ressubheading{Max Plank Institute for the Physics of Complex Systems}{Dresden, Germany}{NSF REU Research Assistant under Prof. Steven Tomsovic}{Summer 2007}

	\begin{itemize}

		\resitem{Research on extreme value statistics in \texttt{MATLAB} and \texttt{FORTRAN}}

	\end{itemize}

\item

	\ressubheading{University of California: Davis}{Davis, CA}{NSF REU Research Assistant under Prof. Daniel Cox}{Summer 2006}

	\begin{itemize}

		\resitem{Computational biophysics research as applied to protein folding in \texttt{Java}}

	\end{itemize}

\end{itemize}

\resheading{Personal}

\begin{itemize}

\item {\bf Hobbies:} Classical Guitar

\item {\bf My Ideal Position:} Working with a fun team solving interesting problems. I enjoy every part of development, from deep backend optimization to client-facing applications and interaction. I would love to make a difference wherever and however I am able while leveraging my machine learning, data mining and mathematical background.

\end{itemize}

\end{document}
